Untitled

### 2022-07-19 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
updating fig s1

colnames(t) <- c("Breeding system","Compatibility system",
         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")

>>>>

t = t %>% select(!Autonomous_selfing_level)

colnames(t) <- c("Breeding system","Compatibility system","Autonomous selfing level", "Flower shape", "Flower symmetry", 
                 "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
                 "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar per flower (microlitres)", "Nectar per flower (miligrames)", "Nectar concentration (%)", "Pollen grains per flower")
